Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-05-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

\medskip
A similar numerical simulation (\ie same geometry, initial mesh resolution, initial and boundary conditions) was also performed using dynamically adaptive mesh. During the simulation, mesh resolution ranged from 235k to 643k \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a). Distinct preferable flow pathways and fingers are shown in Fig.~\ref{fig:3DChannel_severalfields_adapt}b-c and~\ref{fig:3DChannel_satvel_XYplanes_adapt}. Saturation of the wetting fluid during the course of the simulation is shown in Fig.~\ref{fig:3DChannel_sat_adapt}. As expected, both simulations (fixed and adaptive mesh, Figs.~\ref{fig:3DChannel_sat} and~\ref{fig:3DChannel_sat_adapt}, respectively) led to similar results, \ie similar flow pathways and fingers development.

>>>>

\medskip
A similar numerical simulation (\ie same geometry, initial mesh resolution, initial and boundary conditions) was also performed using dynamically adaptive mesh. During the simulation, mesh resolution ranged from 235k to 643k \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_satvel_XYplanes_adapt}a). Distinct preferable flow pathways and fingers are shown in Fig.~\ref{fig:3DChannel_satvel_XYplanes_adapt}b-c and \ref{fig:3DChannel_satvel_XYplanes_adapt}. Saturation of the wetting fluid during the course of the simulation is shown in Fig.~\ref{fig:3DChannel_sat_adapt}. As expected, both simulations (fixed and adaptive mesh, Figs.~\ref{fig:3DChannel_sat} and~\ref{fig:3DChannel_sat_adapt}, respectively) led to similar results, \ie similar flow pathways and fingers development.
